Presentasjon OPX Fiffig tittel

### 2022-08-03 Presentasjon/presentasjon.Rmd
Pres test

# Findings

# Limitations and steps forward

@@

## {data-background="Images/tenke.png" data-background-size=cover}

## <br> Our experience

- Unsolvable case due to non-existent data
- Hard to create credible KPIs due to limited knowledge of economics and the NGO sector
- **Insight into real-life work challenges - the clash between is desired and what is possible**

>>>>

@@

----
```{r, out.height="500", out.width="500", fig.align='center'}
knitr::include_graphics("Images/tenke.png")

## <br> Our experience
- Unsolvable case due to non-existent data
- Hard to create credible KPIs due to limited knowledge of economics and the NGO sector
- **Insight into real-life work challenges - the clash between what is desired and what is possible**
